Molecular Gas \old{Dynamics} \new{Kinematics and Spectral Energy Distribution Properties} of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-12-12 WRITEUP/response.md

"The emission is spatially and dynamically resolved...as shown in Fig. 1 "

"Dynamically resolved" sounds strange. 
The reader might confuse it with the dynamic range.
Maybe change to :

"The line emission is resolved, in both velocity (Fig. 1) and 
in its spatial distribution (Fig. 2).

# RESPONSE:
We have addressed this comment by changing "dynamically resolved" to "kinematically resolved" to minimize potential confusion.

@@

So, they interpret the different magnifications as due to different sizes in the source plane.

This is not the same as magnification varying across the line profile,
due to different source-plane positions, as you are claiming.

# RESPONSE:
We agree with the referee's comment and have changed "dynamical information" to "kinematic information", and "reconstruct the intrinsic gas dynamics" to "reconstruct the intrinsic line profile and source-plane velocity structure".

To address the referee's comment, we have re-written the 2nd paragraph of Section 4.1.2. Rather than saying the differential lensing effect in CO is *similar* to what is seen in the optical, we point out that different magnification factors have been reported in previous studies using optical images. This is done to illustrate the prominence of the differential lensing effect in this source, and to demonstrate that the CO gas traces a different region in the source plane and has a different spatial distribution compared to the stellar populations.

@@

Does Fig.5 now show the spatially integrated spectrum ? 
What is the difference between this spectrum and the one in Fig.1?

If it is again a spectrum taken at the maximum-intensity point,
then the units on the vertical axis would again have to be [ mJy/beam ].

In Fig.5,it would be good to show what you think is the contribution from the companion galaxy.

# RESPONSE:
The referee is correct and we found a bug in the GILDAS package that affected the statistics and fluxes within the map used for previous line-integrated flux extraction. In the resubmitted version, we have updated the intensity reported for CO(2-1) by summing the fluxes over the FWZI (20.3+/-0.6 Jy km/s). The updated intensity is in agreement with the double-Gaussian fitted to the extracted spectrum (Fig. 1). Since the lensing-corrected M_gas for both RXJ1131 and the companion are derived by first summing up the flux density of each channel within the FWZI, and then dividing by their respective magnification factors. This revision in the CO line intensity does not change the conclusions of this paper.

@@

At z = 0.654, 1 arcsec is 7 kpc.

So the de-magnified RADIUS of the CO source is only 3.5 kpc.

It looks like the intrinsic R_CO = 6 kpc (diameter = 12 kpc)
that you quote elsewhere in the paper is too high:
---Abstract, 
---Sect.4.3, para.3, 
---Sect.4.4, para.1, 
---Sect.5.1.1, para.2,
---Sect.5.5, para.2
---Sect.5.1.1, para.2,
---Sect.6, para.2

# RESPONSE:
Source size: 
We addressed the referee's comment on the *deconvolved* CO source size by fitting a single Gaussian in uv-plane, which corresponds to 4.5" +/- 0.1" x 3.5" +/- 0.2", consistent with the reported CO size based on image-plane fitting within the uncertainties. We additionally report the source sizes obtained by fitting two Gaussians to provide further evidence that the CO(2-1) emission is spatially resolved. We have updated Section 3.1 to clarify the discussion.

@@

# RESPONSE
In the residual map, the peak emission is 0.39 +/- 0.08 mJy. This flux (0.39 mJy) is what we adopted for RXJ1131 at 2mm in the paper. To address the referee's comment, we have updated the uncertainty associated with this measurement by adding those associated with the fitted point-source model and that in the residual map (from which we extracted the flux for RXJ1131) in quadrature (i.e. S_2mm = 0.39+/-0.12 mJy).

The emission in the residual is detected at S/N > 4, which is the significance of the emission in the residual map (Data - Model). This together with the fact that this emission is co-spatial with the lensed arc in the optical image indicates that we detect 2mm continuum towards the background source.

To take into account the referee's comment, we have updated the 2mm flux in Table 1, and the flux uncertainty to include those from the uv-fitting process.

The term "deblending" is a broadly used in photometry, and it is clear that it refers to the flux subtraction within the same paragraph. We therefore have seriously considered the referee's suggestions, but have decided to keep the wording as is.

@@

Any comment on the very flat spectrum for the lensing elliptical galaxy ?
Is the 6cm emission mainly synchrotron? 
Is the 2mm emission a mix of synchrotron flux and dust flux ?

# RESPONSE:
While the radio-mm spectral slope of -0.35+/-0.21 derived for the background source has a large error bar associated with it due to the large uncertainty on the 2mm flux (0.39+/-0.12 mJy), the fact that it is significantly flatter than the typical slope for pure synchrotron emission indicates that it provides a limit on the amount of synchrotron emission at 2mm. Thus, we used this radio-mm spectral slope to estimate the expected flux from synchrotron emission at 2mm, and attribute the residual flux to thermal dust emission.Assuming a synchrotron index of alpha = -0.7 and using the 5GHz flux, we expect S_2mmm = 0.122+/-0.004 mJy to be arising from synchrotron emission. We thus find a flux excess of S_2mm = 0.39 - 0.12 = 0.27 mJy that is coming from thermal dust emission. We have updated our dust SED fitting using S_2mm = 0.27+/-0.08 mJy and the resulting parameters throughout the paper.

We note that 0.27+/-0.08 mJy is consistent with our previous flux measurement used for SED fitting (0.39+/-0.12 mJy, including uncertainties from absolute flux calibration) within the uncertainties. Therefore changes to the physical parameters derived from SED fitting are only at most a few percent. We have updated the relevant quantities but this does not alter the conclusions of this paper.

Flat spectrum of foreground galaxy:
We have also added in the paper that if the background source has a contribution in the point-source model assumed in our deblending procedure, such that its flux density would be higher than derived here (0.39 +/- 0.12 mJy), then the derived spectral index (-0.35) would be even shallower.
In this case, the 2mm flux inferred for the foreground galaxy would lower, and thus steepening its spectral slope. Hence, a contribution from the background source to the point-source model 2mm flux may explain the atypical flat spectrum found for the foreground galaxy. Alternatively, the foreground galaxy could be a core-dominated radio objects, and thus displays a flat spectrum.

@@

# RESPONSE:
We have removed the statement regarding "AGN dynamically offset", as suggested by the referee.

1) & 2)
Our CO measurement provides the most precise value for the velocity offset between the BLR and the host galaxy. We thus feel that this is an invaluable addition to the literature.

We acknowledge that velocity offsets between BLR and NLR lines are quite common in Seyferts and quasars, but the offsets as large as that of RXJ1131 appear to be uncommon according to the distribution of offset among other AGN hosts (Richards+02, Bonning+07). To take into account the referee's comments, we have updated this section by including a brief discussion on other possible interpretations for the velocity offset (e.g. gas inflows, geometric effects), as outlined in detail by the referee.

We agree with the referee that it is unlikely that all offsets in AGN lines are caused by black hole recoil. Considering the referee's comments, we have updated this section to discuss other possible scenarios as well. We only discuss the recoiling black hole as one of the possibility interpretations for the velocity offset, given that 
i) the magnitude of the offset in RXJ1131 (>700 km/s) appears to be an outlier in the distribution of offset found for large samples of QSOs (Richards+02, Bonning+07).
ii) RXJ1131 appears to have a high BH spin parameter (a > 0.9; Reis+14). 
iii) recoiling BHs are expected theoretically from hierarchical model of galaxy evolution.

3)
The BH displacement estimated by the referee (~few 10kpc) has been shown to be theoretically possible in the absence of dynamical friction (Bonning+07, Loeb 2007). However, Loeb 2007 has shown that at low ejection speeds of a few hundred km/s, the recoil is expected to be damped by the external gravitational potential of the galaxy, dynamical friction against background stars, dark matter, and gas, thereby limiting the BH displacement and is likely to bring it back to the center of its host galaxy within a few dynamical times (Madau & Quataert 04, Boylan-Kolchin+04, Guedes+11).

### 2016-12-12 WRITEUP/diff.tex
with DR's comment and changed focus of conclusion to feedback

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and \eq(2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\pmm4\%} inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, $M_{\rm dust}$\ssim\old{4}\new{3}\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of \old{\mbox{$>$0.27\petm{11}{8}\%}} \new{$>$0.27\petm{0.11}{0.08}\%} which is higher
than the
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

\subsection{PdBI \bco}
\old{Observations of the \mbox{\bco} rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
at the $\nu_{\rm LO}$\eq139.256\,GHz
were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
Riechers).} 
\new{Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
towards RXJ1131
were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
Riechers).
Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.}
Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission towards the background source RXJ1131 in the PdBI data
at $\gtrsim$\,27$\sigma$ significance\old{, confirming the redshift at $z_{\rm CO}$ =
0.6537\,$\pm$\,0.0005.} 
\new{. Based on this measurement, we refine the redshift of RXJ1131 to
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\mbox{\footnote{This redshift is derived by fitting a double-Gaussian to 
the de-lensed spectrum (\Fig{delensed}) 
instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
redshift determination 
due to differential lensing (see \Sec{differential}).
}.}}
The emission is spatially and \old{dynamically}\new{kinematically} resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is \old{24.1\,$\pm$\,2.3 Jy \kms}\new{20.3\,$\pm$\,0.6 Jy \kms}.

@@

\old{The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
the image plane
is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as a two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, therefore we take this as an estimate on the full extent of the lensed
emission. On the other hand, if we assume that the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \mbox{\nir}
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and
the lensed knots \mbox{(see \Fig{CO21mom}).}}
\new{The deconvolved source size FWHM obtained from fitting a single two-dimensional Gaussian 
to the integrated line emission in the image plane yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  
which is consistent with that obtained by visibility-plane fitting within the uncertainties. 
Since the spatial distribution of the observed CO emission is unlikely to be fully described by a simple Gaussian
and appears to be a superposition of two components (top left panel of \Fig{CO21mom}), 
we also fit two Gaussians to the intensity map. 
This yields deconvolved source sizes of 
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
The deconvolved source sizes of both models suggest that the gravitationally lensed CO emission is more extended 
than the optical 
``Einstein ring'', which has a diameter of $\sim$3\farcs6
(i.e., the ``Einstein ring'' formed by CO emission is likely to have a larger diameter compared to the optical one). 
This is consistent with the centroid position of the redshifted emission, which is along the quasar arc seen in the optical image, 
and the blueshifted emission, which is offset further to the SE (top right of \Fig{CO21mom}).
Therefore, the CO-emitting region in RXJ1131 is likely to be more extended than its stellar and quasar emission.}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
\old{The spectrum is shown in \mbox{\Fig{co32spec}} and appears to be consistent with a
double-peaked profile. }
\new{The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \mbox{\Fig{co32spec}}, where
we over-plot spectra of the \bco and \cco lines.
We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, indicating a $\gtrsim$3$\sigma$ detection for this component alone, and a peak line flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing, 
indicating a $\sim$\,6$\sigma$ detection. }
We estimate a line intensity of 
\old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms (\mbox{\Tab{obsprop}})}
by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity.

@@

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and the core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc with their centroids
coincident with the optical emission from the quasar.
We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
\old{We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
for the foreground
galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.345
for the background galaxy by fitting a
power-law ($S_\nu \propto \nu^{\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.}
\new{We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02\pmm0.07
for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35\pmm0.21 % differential
for the background galaxy by fitting
power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum fluxes at
5\,GHz and 2\,mm. 
The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \mbox{\citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}}. This likely suggests % {\bf DR: 3C273 flat-spectrum radio source BLAH}
that a fraction of the observed 2\,mm emission arises from thermal dust  emission. 
This spectral slope would be even shallower 
if the background source contributes to the unresolved fraction of the
2\,mm flux. This would also 
explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies. 
Assuming a synchrotron slope of $\alpha$\ssim$-$0.7, we would expect
a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm
and thus an excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy relative to this expectation
likely arises due to thermal dust emission.
}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.45\textwidth]{../Figures/de-lensedSpecCO21_complicated_unbinned_ylog.eps}
\caption{Top: the full resolution \bco spectrum (yellow histogram) and
the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The light
blue histogram shows the ``intrinsic'' line profile of RXJ1131
after subtracting a contribution from its companion galaxy and
correcting for lensing using the magnification factor $\mu_{\rm L}$ as annotated by the horizontal bar shown
above each respective model channel.
\new{Bottom: the ``intrinsic'' line profile of RXJ1131 (light blue) and of its companion (dark blue).
The y-axis is shown on log scale (top) and linear scale (bottom).}
\label{fig:delensed}}
\end{figure}

@@

\old{Similar to previous studies of RXJ1131, where
differential lensing across the {\it HST}
$V$-, $I$-, and $H$-bands has been detected with a
magnification factor decreasing from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}},
the highly asymmetric \mbox{\bco} line profile suggests that
differential lensing is also non-negligible for CO,
causing the redshifted emission to be apparently much brighter than the
blueshifted component.
This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model}}) and also partly due to a contribution from the companion in the redshifted velocity channels.}
\new{Previous studies of RXJ1131 find evidence for differential lensing across 
the {\it HST} $V$-, $I$-, and $H$-bands, where the
magnification factor varies from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}}.
This indicates that emission from different stellar populations 
within the host galaxy are dissimilar with respect to the caustic. 
%This imply that different stellar populations in the host galaxy are not co-spatial, and have  
%different spatial extents, or
%may be a result of dust extinction and reddening.
The best-fit lens models obtained here for different CO channels show that differential lensing also plays 
an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
from 8.7 to 3.1 across different kinematic components (\mbox{\Tab{model}}).
The asymmetry in the line profile (\Fig{CO21spec} and \Fig{delensed}) is therefore predominantly a result of
the redshifted CO-emitting gas being more strongly-magnified 
than the 
blueshifted component.
A secondary effect is likely a result of including emission from the companion in the most redshifted velocity channels.}
The variation in $\mu_{\rm L}$ found across channels is consistent with the source-plane
positions relative to the caustics in \Fig{model}, where the red wing
emission mainly originates near the cusp
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}).

@@

\subsubsection{Gas Mass Fractions and Gas-to-dust Ratio}

>>>>

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\pmm4\%} is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
\old{We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
\mbox{$M_{*}$\eq(3\pmm1)\E{10}\,\Msun}, \mbox{$M_{\rm dust}$\ssim3\E{8}\,\Msun}, \mbox{$L_{\rm IR}$\ssim1.5\E{12}\,\Lsun}, and \mbox{SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU} for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} which is higher
than the
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.}
\new{We find a lensing-corrected stellar mass of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU, and
a star formation efficiency and specific SFR comparable to non-quasar host galaxies at $z$\ssim1.
This together with a gas mass fraction consistent with the trend of evolution indicate 
that no quenching of star formation is seen in RXJ1131.
Our results therefore suggest that 
the decrease in molecular gas mass fraction towards lower redshift 
plays a dominant role 
in the decline of cosmic star formation history even in quasar host galaxies.}
\end{abstract}

@@

\subsection{PdBI \bco}
\old{Observations of the \mbox{\bco} rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
at the $\nu_{\rm LO}$\eq139.256\,GHz
were carried out using the IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
Riechers).} 
\new{Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
towards RXJ1131
were carried out using IRAM \mbox{\pdbi} (PdBI; Program ID: S14BX; PI: D.
Riechers).
Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.}
Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission towards the background source RXJ1131 in the PdBI data
at $\gtrsim$\,27$\sigma$ significance\old{, confirming the redshift at $z_{\rm CO}$ =
0.6537\,$\pm$\,0.0005.} 
\new{. Based on this measurement, we refine the redshift of RXJ1131 to
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002}\footnote{This redshift is derived by fitting a double-Gaussian to 
the de-lensed spectrum (\Fig{delensed}) 
instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
redshift determination 
due to differential lensing (see \Sec{differential}).}
The emission is spatially and \old{dynamically}\new{kinematically} resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is \old{24.1\,$\pm$\,2.3 Jy \kms}\new{20.3\,$\pm$\,0.6 Jy \kms}.

@@

\old{The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
the image plane
is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as a two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, therefore we take this as an estimate on the full extent of the lensed
emission. On the other hand, if we assume that the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \mbox{\nir}
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and
the lensed knots \mbox{(see \Fig{CO21mom}).}}
\new{The deconvolved source size FWHM obtained from fitting a single two-dimensional Gaussian 
to the integrated line emission in the image plane yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  
which is consistent with that obtained by visibility-plane fitting within the uncertainties. 
Since the spatial distribution of the observed CO emission is unlikely to be fully described by a simple Gaussian
and appears to be a superposition of at least two components (top left panel of \Fig{CO21mom}), 
we also fit two Gaussians to the intensity map. 
This yields deconvolved source sizes of 
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, separated 
by $\sim$2\farcs2 in RA and $\sim$1\farcs7 in Dec.  % ((3-0.76)^2+(2.49-.78)^2)^.5
The deconvolved source sizes of both models suggest that the gravitationally lensed CO emission is more extended 
than the optical 
``Einstein ring'', which has a diameter of $\sim$3\farcs6
(i.e., the ``Einstein ring'' formed by CO emission is likely to have a larger diameter compared to the optical one). 
This is consistent with the centroid position of the redshifted emission, which is along the quasar arc seen in the optical image, 
and the blueshifted emission, which is offset further to the SE (top right of \Fig{CO21mom}).
Therefore, the CO-emitting region in RXJ1131 is likely to be more extended than its stellar and quasar emission.}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
\old{The spectrum is shown in \mbox{\Fig{co32spec}} and appears to be consistent with a
double-peaked profile. }
\new{The \cco spectrum appears to be consistent with a double-peaked profile, as shown in \mbox{\Fig{co32spec}}, where
we over-plot spectra of the \bco and \cco lines.
We extract the peak fluxes and their corresponding uncertainties for the blue and red wing independently.
We find a peak line flux of 5.13\pmm1.43 Jy\,\kms beam\pmOne for the blue wing, indicating a $\gtrsim$3$\sigma$ detection for this component alone, and a peak line flux of 11.45\pmm1.99\,Jy\,\kms beam\pmOne for the red wing, 
indicating a $\sim$\,6$\sigma$ detection. }
We measure a line intensity of 
\old{35.7\,$\pm$\,21.9 Jy\,\kms} \new{35.7\,$\pm$\,6.9\,Jy\,\kms (\mbox{\Tab{obsprop}})}
by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity.

@@

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and the core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc with their centroids
coincident with the optical emission from the quasar.
We extract the flux densities for the lensing arc and the radio core in \Tab{photometry}.
\old{We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.024
for the foreground
galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.345
for the background galaxy by fitting a
power-law ($S_\nu \propto \nu^{\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.}
\new{We find a spectral index of $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.02\pmm0.07
for the foreground galaxy and $\alpha^{\rm 2mm}_{\rm 6cm}$\,=\,$-$0.35\pmm0.21 % differential
for the background galaxy by fitting
power-laws ($S_\nu \propto \nu^{\alpha}$) to their continuum fluxes at
5\,GHz and 2\,mm. 
The spectral slope derived for the background source is flatter than the typical slope of pure synchrotron emission \mbox{\citep[$\alpha$\ssim$-$0.7; e.g.,][]{Andreani93a}}. This likely suggests 
that at least a fraction of the observed 2\,mm emission arises from thermal dust emission. 
This spectral slope would be even shallower 
if the background source contributes to the unresolved fraction of the
2\,mm flux. 
In this case, the 2\,mm flux of the foreground galaxy would be lower than the value reported here and yield a steeper slope.
This would also explain the flat spectrum found for the foreground galaxy, which is atypical of elliptical galaxies. 
Assuming a spectral slope of $\alpha$\ssim$-$0.7 for synchrotron radiation in RXJ1131, we expect
a flux density of $S_{\rm 2mm}$\eq0.122\pmm0.004 mJy at 2\,mm. 
The flux excess of $S_{\rm 2mm}$\eq0.27\pmm0.08\,mJy therefore likely arises due to thermal dust emission.
}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.45\textwidth]{../Figures/de-lensedSpecCO21_complicated_unbinned_ylog.eps}
\caption{Top: the full resolution \bco spectrum (yellow histogram) and
the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The light
blue histogram shows the ``intrinsic'' line profile of RXJ1131
after subtracting a contribution from its companion galaxy and
correcting for lensing using the magnification factor $\mu_{\rm L}$ as annotated by the horizontal bar shown
above each respective model channel.
\new{Bottom: the ``intrinsic'' line profile of RXJ1131 (light blue) and of its companion (dark blue).
The y-axes are shown on a log scale.}
\label{fig:delensed}}
\end{figure}

@@

\old{Similar to previous studies of RXJ1131, where
differential lensing across the {\it HST}
$V$-, $I$-, and $H$-bands has been detected with a
magnification factor decreasing from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}},
the highly asymmetric \mbox{\bco} line profile suggests that
differential lensing is also non-negligible for CO,
causing the redshifted emission to be apparently much brighter than the
blueshifted component.
This can be explained by the difference in magnification factor $(\mu_{\rm L})$ which
varies from 8.7 to 3.1 across the \mbox{\bco} line (\mbox{\Tab{model}}) and also partly due to a contribution from the companion in the redshifted velocity channels.}
\new{Previous studies of RXJ1131 find evidence for differential lensing across 
the {\it HST} $V$-, $I$-, and $H$-bands, where the
magnification factor varies from 10.9 to 7.8 \mbox{\citepalias{Claeskens06a}}.
This indicates that the emission from different stellar populations 
within the host galaxy 
have various spatial extents and positions with respect to the caustic. 
%This imply that different stellar populations in the host galaxy are not co-spatial, and have  
%different spatial extents, or
%may be a result of dust extinction and reddening.
The best-fit lens models obtained here for different CO channels show that differential lensing also plays 
an important role in the observed \bco emission, with a magnification factor $(\mu_{\rm L})$ that varies
from 8.7 to 3.1 across different kinematic components (\mbox{\Tab{model}}).
The asymmetry in the line profile (\Fig{CO21spec} and \Fig{delensed}) is therefore predominantly a result of
the redshifted CO-emitting gas being more strongly-magnified 
than the 
blueshifted component.
A secondary reason is likely due to 
the inclusion of the emission of the companion in the most redshifted velocity channels.}
The variation in $\mu_{\rm L}$ found across channels is consistent with the source-plane
positions relative to the caustics in \Fig{model}, where the red wing
emission mainly originates near the cusp
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
are $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively,
implying an intrinsically symmetric line profile (\Fig{delensed}). This is consistent with the symmetric source-plane
velocity gradient in our lens model (\Fig{model} and \Fig{PV}).

@@

\subsubsection{Gas Mass Fractions and Gas-to-dust Ratio} \label{sec:frac}
